\chapter{Updates}
\section{Updates respect initial planning}
\subsection{About tasks and time planification}
\subsubsection*{Changes}
Regarding the initial planning of the project, there have not been very big changes.
The main change has been that I have needed more investment of time in understanding the library and in coding the word counting problem.
This is because I have found the need to make several adaptations to the library to allow more options and be able to implement my initial problem.
Everything and so I have only needed 2 extra week in the overall time of the \textbf{RL} and \textbf{FA} sections.

In addition to this, I have been able to specify with Edelmira what improvements I can make to the library.
This process was also planned for later, so it also changes the planning a bit.

\subsubsection*{Consequences}
All these changes in planning mean that there is less time left to perform the following tasks (SA, D3, D4).
But at the same time I have invested more time getting to know the library and programming, so I foresee that it will take me less time to improvements to the library that Edelmira proposes. 

\subsubsection*{New planning}
With this updates, the new planning is as follows:
\newpage

\definecolor{LightGray}{rgb}{0.8,0.8,0.8}
\begin{table}[H]
    \begin{adjustwidth}{-1in}{-1in}
    \centering
    \begin{tabular}{|p{5cm}|c|c|p{2cm}|p{3cm}|p{3cm}|}
    \hline
    \textbf{Description} & \textbf{TAG} & \textbf{Hours} & \textbf{Previous Tasks} & \textbf{Requirements} & \textbf{Human Resource} \\
    \hline
    \hline	
    \rowcolor{LightGray}
    \textbf{Project definition and planning} & \textbf{G} & \textbf{75} & \textbf{-} & \textbf{-} & \textbf{-}  \\
    \hline
    Context and Scope & G1 & 20 & Laptop & None & None \\
    \hline
    Planning & G2 & 12 & G1 & Laptop & GEP Tutor \\
    \hline
    Budget and Sustainability & G3 & 18 & G2 & Laptop & GEP Tutor \\
    \hline
    Final Document & G4 & 25 & G3 & Laptop & GEP Tutor \\
    \hline
    \hline
    \rowcolor{LightGray}
    \textbf{Research and Learning} & \textbf{RL} & \cancel{\textcolor{red}{75}} 95 & \textbf{G} & \textbf{-} & \textbf{-} \\
    \hline
    Haskell Refresh & RL1 & 20 & None & Laptop, Books & Supervisor \\
    \hline
    TFM assimilation & RL2 & \cancel{\textcolor{red}{25}} 15& None & Laptop & Supervisors \\
    \hline
    Dynamic Pipeline Framework & RL3 & \cancel{\textcolor{red}{30}} 60 & RL1, RL2 & Laptop & Juan Pablo \\
    \hline
    \hline
    \rowcolor{LightGray}
    \textbf{First Algorithm Development} & \textbf{FA} & \cancel{\textcolor{red}{80}} \textbf{100}  & \textbf{RL} & \textbf{-} & \textbf{-} \\
    \hline
    Algortim Scaffold & FA1 & 20 & None & None & Supervisors\\
    \hline
    Algorith Implementation & FA2 & \cancel{\textcolor{red}{50}} 70 & FA1 & Laptop & Supervisor\\
    \hline
    Algorithm Testing & FA3 & 10 & FA2 & Laptop & None \\
    \hline
    \hline
    \rowcolor{LightGray}
    \textbf{Second Algorithm Development} & \textbf{SA} & \cancel{\textcolor{red}{130}} \textbf{90}  & \textbf{FA} & \textbf{-} & \textbf{-} \\
    \hline
    Finding Weak Points & SA1 & \cancel{\textcolor{red}{15}} 10 & None & Laptop & Co-supervisor\\
    \hline
    Improvement Scaffolds & SA2 & \cancel{\textcolor{red}{15}} 10 & SA1 & None & None\\
    \hline
    Algorith Implementation & SA3 & \cancel{\textcolor{red}{80}} 50 & SA2 & Laptop & Supervisor\\
    \hline
    Algorithm Testing & SA4 & 20 & SA3 & Laptop & None\\
    \hline
    \hline
    \rowcolor{LightGray}
    \textbf{Documentation} & \textbf{D} & \textbf{100} & \textbf{RL,FA,SA,G} & \textbf{-} & \textbf{-} \\
    \hline
    Documentation of RL section & D1 & 10 & RL & Laptop & None \\
    \hline
    Documentation of FA section & D2 & 20 & FA & Laptop & None \\
    \hline
    Documentation of SA section & D3 & 20 & SA & Laptop & None \\
    \hline
    Final Documentation & D4 & 50 & D1, D2, D3 & Laptop & Supervisors \\
    \hline
    \hline
    \rowcolor{LightGray}
    \multicolumn{6}{|c|}{\textbf{Total (G + RL + FA + SA + D): 460 hours}}  \\
    \hline
    \end{tabular}
    \caption{Summary of Project Planning, self elaborated}
    \label{TableResume}
    \end{adjustwidth}
\end{table}

\subsection{About scope}
\subsubsection*{Changes}
Since initially planning the scope of my work, I have had to modify it as I have progressed.
The reason is that when working with the Haskell library, I have encountered some lack of functionality at some points.
I have found that Juan Pablo made a very complete library but a little oriented to his work.
That's why when trying to implement the word counting problem, I have had to expand and create new functionalities. 

\subsubsection*{Consequences}
No several consequences have been derived from this change.
Just that I have had to invest more time in understanding the library, as reflected in the previous section.
\subsection{About budget}
\subsubsection*{Changes}
Because the scope and time planification changes, budged has also changed. 
The human resource budged needs to be recalculated tacking into account the new time planification. 
The other sections of the budget like hardware, software and unexpected const remain the same.
\subsubsection*{Consequences}
As we can apreciete in the table below, the new human resource budget is less that 0,5\% higher than the initial budget, so the changes are not significant. 
\subsubsection*{New Budget} 
\begin{table}[H]
    \begin{adjustwidth}{-1in}{-1in} % Adjust margins by -1 inch on both sides
    \centering
    \begin{tabular}{|c|c|c|c|c|}
    \hline
    \textbf{Role} & \textbf{Avg. Salary (€/h)} & \textbf{Hours} & \textbf{Total (€)} & \textbf{Total with Social Security (€)} \\ 
    \hline
    Researcher & 15 & \cancel{\textcolor{red}{85}} 75 hours & \cancel{\textcolor{red}{1275}} 1125 & \cancel{\textcolor{red}{1657.5}} 1462.5\\
    \hline
    Haskell Developer & 18 & \cancel{\textcolor{red}{200}} 210 hours & \cancel{\textcolor{red}{3600}} 3780 & \cancel{\textcolor{red}{4680}} 4914\\
    \hline
    Project Manager & 20 & 175 hours & 3500 & 4550\\
    \hline
    \hline
    \textbf{Total} & \cancel{\textcolor{red}{18.2}} 18.3 & 460 & \cancel{\textcolor{red}{8375}} 8405 & \cancel{\textcolor{red}{10887.5}} 10926.5\\
    \hline
    \end{tabular}
    \caption{New Human Resources Cost, self elaborated}
    \label{new_human_resources}
    \end{adjustwidth}
\end{table} 

\begin{table}[H]
    \begin{adjustwidth}{-1in}{-1in} % Adjust margins by -1 inch on both sides
    \centering
    \begin{tabular}{|c|c|}
    \hline
    \textbf{Source} & \textbf{Cost (€)} \\ 
    \hline
    Hardware &  55,29 \\
    \hline
    Software & 0 \\
    \hline
    Human Resources & \cancel{\textcolor{red}{10887.5}} 10926.5 \\
    \hline
    Unexpected & 2037 \\
    \hline
    \hline
    \textbf{Total} & \cancel{\textcolor{red}{12979.79}} \textbf{13018.79}  \\
    \hline
    \end{tabular}
    \caption{New total budget, self elaborated}
    \label{new_total_budget}
    \end{adjustwidth}
\end{table}

\section{Laws and regulations}
Consulting the BOE, law 14/2011, updated on 01/11/2023, article 15 (page 28) tells us about various obligations of the researcher and here I will comment on those that involve me \cite{}
\subsection*{Avoid plagiarism and misappropriation of authorship of scientific works or third-party technologies}
On this point, I have at all times cited other people's resources and whenever I have used a third-party technological resource I have made sure that it is open source and that its necessary citations are made.

\subsection*{Inform the entities for which it provides services of all the findings, discoveries and results susceptible to legal protection, and collaborate in the processes of protection and transfer of the results of their investigations}
At all times I have been in contact with my director and have been reporting on my work.

\subsection*{Disseminate the results of your investigations, if applicable, as indicated in this law, so that the results are used through communication and transfer to other research, social or technological contexts, and if applicable, for their marketing and valuation. In particular, the research staff must ensure and take the initiative so that its results generate social value}
This work will be public once finished and everyone will be able to take advantage of the discoveries.

\subsection*{Ensure that your work is relevant to society}
This work can help expand resources on dynamic pipeline and Haskell code.

\subsection*{Use the name of the entities for which you provide services in the realization of its scientific activity, in accordance with the internal regulations of said entities and the agreements, pacts and conventions that they subscribe}
On the cover of this work you will find at all times the name of the entity (UPC) and the faculty (FIB) as well as their logos. 

\subsection*{Adopt the necessary measures to comply with the applicable regulations in matters of data protection and confidentiality}
At all times, we are ensuring compliance with data protection, always using data that is free to use and that complies with the laws.